Determining multi-scale controls on river temperature: a time series approach

### 2017-04-18 manuscript/manuscript.tex
added some notes to the manuscript
converted tex to docx, fixed a few small things

%add to appendix A: trends and loadings from 2-trend model

@@

\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/01_trends_simple.pdf}}
\end{center}
\textbf{Figure A6} Shared trends from simplified model (no seasonal fixed factor, no snowmelt predictor)

\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/02_loadings_simple.pdf}}
\end{center}
\textbf{Figure A7} Factor loadings from simplified model (no seasonal fixed factor, no snowmelt predictor)

>>>>

%add to appendix A: trends and loadings from 2-trend model
%do a comparison of loadings and effect sizes. find the major players
%make sure x axes of regression plots arent missing numeric labels
%talk about comparisons between effect sizes: i.e. air temperature is the dominant climatic factor
%incorporate ashley steele paper on relationship between sun, water, aid

@@

\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/01_trends_simp.pdf}}
\end{center}
\textbf{Figure A6} Shared trends from simplified model (no seasonal fixed factor, no snowmelt predictor)

\begin{center}
\resizebox{\textwidth}{!}{\includegraphics{figures/diagnostic_plots/02_loadings_simp.pdf}}
\end{center}
\textbf{Figure A7} Factor loadings from simplified model (no seasonal fixed factor, no snowmelt predictor)
